---
title: "Results Reliability Generalization and Variance Decomposition"
author: "Lukas Beinhauer"
format: html
editor: visual
---


```{r}

paths_rel <- list.files(file.path("Data/Reliability Estimates"), full.names = TRUE)

paths_alpha <- paths_rel[grep("_Alpha.csv$", paths_rel)]

alpha_estimates.list <- lapply(paths_alpha, FUN = function(x){read.csv(x)})



Alpha_rma.list <- readRDS(file.path("Data/Shiny Data/Alpha_rma.list.RData"))
Bonett.Alpha_rma.list <- readRDS(file.path("Data/Shiny Data/Bonett.Alpha_rma.list.RData"))

varT_est.list <- readRDS(file.path("Notes/bootstrapped_varT.RData"))
varE_est.list <- readRDS(file.path("Notes/bootstrapped_varE.RData"))

varT_rma.list <- readRDS(file.path("Notes/bootstrapped_varT_rma.RData"))
varE_rma.list <- readRDS(file.path("Notes/bootstrapped_varE_rma.RData"))



```

```{r}

s_Caciop_Alpha <- summary(alpha_estimates.list[[1]]$Reliability)

r.dec <- 3

s_Caciop_Alpha_rma <- Alpha_rma.list[[1]]
s_Caciop_B.Alpha_rma <- Bonett.Alpha_rma.list[[1]]

s_Caciop_varT <- summary(varT_est.list[[1]]$var.est)
s_Caciop_varE <- summary(varE_est.list[[1]]$var.est)

s_Caciop_varT_rma <- varT_rma.list[[1]]
s_Caciop_varE_rma <- varE_rma.list[[1]]





s_ShnabelRPP_Alpha <- summary(alpha_estimates.list[[9]]$Reliability)

s_ShnabelRPP_Alpha_rma <- Alpha_rma.list[[9]]
s_ShnabelRPP_B.Alpha_rma <- Bonett.Alpha_rma.list[[9]]

s_ShnabelRPP_varT <- summary(varT_est.list[[9]]$var.est)
s_ShnabelRPP_varE <- summary(varE_est.list[[9]]$var.est)

s_ShnabelRPP_varT_rma <- varT_rma.list[[9]]
s_ShnabelRPP_varE_rma <- varE_rma.list[[9]]




s_ShnabelRev_Alpha <- summary(alpha_estimates.list[[8]]$Reliability)

s_ShnabelRev_Alpha_rma <- Alpha_rma.list[[8]]
s_ShnabelRev_B.Alpha_rma <- Bonett.Alpha_rma.list[[8]]

s_ShnabelRev_varT <- summary(varT_est.list[[8]]$var.est)
s_ShnabelRev_varE <- summary(varE_est.list[[8]]$var.est)

s_ShnabelRev_varT_rma <- varT_rma.list[[8]]
s_ShnabelRev_varE_rma <- varE_rma.list[[8]]

```

## Results Reliability Generalization and Variance Decomposition

### Cacioppo

Data set 1 concerned the scale of Need for Cognition (Cacioppo & Petty, 1982), consisting of 6 Likert-stye items (5-point scale). Measured across 21 labs in Ebersole et al. (2016), using Cronbach’s Alpha, score reliability varied between `r round(s_Caciop_Alpha[1], r.dec)` and `r round(s_Caciop_Alpha[6], r.dec)`, with a mean value of `r round(s_Caciop_Alpha[4], r.dec)` and median value `r round(s_Caciop_Alpha[3], r.dec)`. Performing a random-effects meta-analysis on the untransformed Cronbach’s Alpha estimates, we find a meta-analytic mean estimate of `r round(s_Caciop_Alpha_rma$b[1], r.dec)` (`r round(s_Caciop_Alpha_rma$ci.lb, r.dec)` : `r round(s_Caciop_Alpha_rma$ci.ub, r.dec)`). Additionally, we find a significant degree of heterogeneity in score reliability, at Q(`r s_Caciop_Alpha_rma$k - 1`) = `r round(s_Caciop_Alpha_rma$QE, r.dec)`, p `r ifelse(s_Caciop_Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_Caciop_Alpha_rma$QEp, r.dec)))`. In terms of I^2, heterogeneity is `r round(s_Caciop_Alpha_rma$I2, r.dec)`%, which, according to XXX constitutes a large level of heterogeneity. In terms of tau, we find a standard deviation of `r round(sqrt(s_Caciop_Alpha_rma$tau2), r.dec)` in true values of Cronbach’s Alpha. Similarly, when assessing Bonett-transformed Cronbach’s Alpha estimates, we find a meta-analytic mean of `r round(s_Caciop_B.Alpha_rma$b[1], r.dec)`. Back-transformed this constitutes a Cronbach’s Alpha of `r round(1-exp(s_Caciop_B.Alpha_rma$b[1]), r.dec)` (CI: `r round(1-exp(s_Caciop_B.Alpha_rma$ci.ub), r.dec)` : `r round(1-exp(s_Caciop_B.Alpha_rma$ci.lb), r.dec)`) (difference in MA-est. emerges at the 3rd decimal). Heterogeneity in Bonett-transformed estimates of Cronbach’s Alpha is also of statistically significant degree: Q(`r s_Caciop_Alpha_rma$k - 1`) = `r round(s_Caciop_B.Alpha_rma$QE, r.dec)`, p `r ifelse(s_Caciop_B.Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_Caciop_B.Alpha_rma$QEp, r.dec)))`. Standardized heterogeneity estimates of I^2 = `r round(s_Caciop_B.Alpha_rma$I2, r.dec)`% and H^2 = `r round(s_Caciop_B.Alpha_rma$H2, r.dec)` display highly similar amounts of heterogeneity. When using McDonald’s Omega to estimate score reliability, the results change only to a very small degree. Therefore, estimates using McDonald’s Omega can be found in the supplemental materials.


Also, we use Cronbach's Alpha to decompose the observed variance into its true and error score variance components:

{}  | True Score Variance | Error Score Variance
-- | -- | --: 
Min | `r round(s_Caciop_varT[1], r.dec)` | `r round(s_Caciop_varE[1], r.dec)`
Q1  | `r round(s_Caciop_varT[2], r.dec)` | `r round(s_Caciop_varE[2], r.dec)`
Median| `r round(s_Caciop_varT[3], r.dec)` | `r round(s_Caciop_varE[3], r.dec)`
Q3  | `r round(s_Caciop_varT[4], r.dec)` | `r round(s_Caciop_varE[4], r.dec)`
Max | `r round(s_Caciop_varT[5], r.dec)` | `r round(s_Caciop_varE[5], r.dec)`
Mean| `r round(s_Caciop_varT[6], r.dec)` | `r round(s_Caciop_varE[6], r.dec)`

Performing a random-effects meta-analysis on the components directly leads to:

{} | True Score Variance | Error Score Variance
-- | -- | --:
Meta-Analytic Mean Estimate | `r round(s_Caciop_varT_rma$b[1], r.dec)` | `r round(s_Caciop_varE_rma$b[1], r.dec)`
Confidence Interval | `r round(s_Caciop_varT_rma$ci.lb, r.dec)` : `r round(s_Caciop_varT_rma$ci.ub, r.dec)` | `r round(s_Caciop_varE_rma$ci.lb, r.dec)` : `r round(s_Caciop_varE_rma$ci.ub, r.dec)`
Heterogeneity tau | `r round(sqrt(s_Caciop_varT_rma$tau2), r.dec)` | `r round(sqrt(s_Caciop_varE_rma$tau2), r.dec)`
Heterogeneity I^2 | `r round(s_Caciop_varT_rma$I2, r.dec)` | `r round(s_Caciop_varE_rma$I2, r.dec)`
Heterogeneity H^2 | `r round(s_Caciop_varT_rma$H2, r.dec)` | `r round(s_Caciop_varE_rma$H2, r.dec)`
Q(`r s_Caciop_varT_rma$k - 1`) | `r round(s_Caciop_varT_rma$QE, r.dec)` | `r round(s_Caciop_varE_rma$QE, r.dec)`
p-value QE | `r ifelse(s_Caciop_varT_rma$QEp < .001, "<.001", round(s_Caciop_varT_rma$QEp, r.dec))` | `r ifelse(s_Caciop_varE_rma$QEp < .001, "<.001", round(s_Caciop_varE_rma$QEp, r.dec))`



### Shnabel Sense of Power (RPP)


Data set 2 concerned the scale of Sense of Power (Shnabel & Nadler, 2008), consisting of 3 Likert-stye items (7-point scale). Measured across 8 labs in Baranski et al. (2020), using Cronbach’s Alpha, specifically for those labs following the RPP-protocol, score reliability varied between `r round(s_ShnabelRPP_Alpha[1], r.dec)` and `r round(s_ShnabelRPP_Alpha[6], r.dec)`, with a mean value of `r round(s_ShnabelRPP_Alpha[4], r.dec)` and median value `r round(s_ShnabelRPP_Alpha[3], r.dec)`. Performing a random-effects meta-analysis on the untransformed Cronbach’s Alpha estimates, we find a meta-analytic mean estimate of `r round(s_ShnabelRPP_Alpha_rma$b[1], r.dec)` (`r round(s_ShnabelRPP_Alpha_rma$ci.lb, r.dec)` : `r round(s_ShnabelRPP_Alpha_rma$ci.ub, r.dec)`). Additionally, we find a significant degree of heterogeneity in score reliability, at Q(`r s_ShnabelRPP_Alpha_rma$k - 1`) = `r round(s_ShnabelRPP_Alpha_rma$QE, r.dec)`, p `r ifelse(s_ShnabelRPP_Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_ShnabelRPP_Alpha_rma$QEp, r.dec)))`. In terms of I^2, heterogeneity is `r round(s_ShnabelRPP_Alpha_rma$I2, r.dec)`%, which, according to XXX constitutes a medium level of heterogeneity. In terms of tau, we find a standard deviation of `r round(sqrt(s_ShnabelRPP_Alpha_rma$tau2), r.dec)` in true values of Cronbach’s Alpha. Similarly, when assessing Bonett-transformed Cronbach’s Alpha estimates, we find a meta-analytic mean of `r round(s_ShnabelRPP_B.Alpha_rma$b[1], r.dec)`. Back-transformed this constitutes a Cronbach’s Alpha of `r round(1-exp(s_ShnabelRPP_B.Alpha_rma$b[1]), r.dec)` (CI: `r round(1-exp(s_ShnabelRPP_B.Alpha_rma$ci.ub), r.dec)` : `r round(1-exp(s_ShnabelRPP_B.Alpha_rma$ci.lb), r.dec)`) (difference in MA-est. emerges at the 3rd decimal). Heterogeneity in Bonett-transformed estimates of Cronbach’s Alpha is also of statistically significant degree: Q(`r s_ShnabelRPP_Alpha_rma$k - 1`) = `r round(s_ShnabelRPP_B.Alpha_rma$QE, r.dec)`, p `r ifelse(s_ShnabelRPP_B.Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_ShnabelRPP_B.Alpha_rma$QEp, r.dec)))`. Standardized heterogeneity estimates of I^2 = `r round(s_ShnabelRPP_B.Alpha_rma$I2, r.dec)`% and H^2 = `r round(s_ShnabelRPP_B.Alpha_rma$H2, r.dec)` display highly similar amounts of heterogeneity. 


Also, we use Cronbach's Alpha to decompose the observed variance into its true and error score variance components:

{}  | True Score Variance | Error Score Variance
-- | -- | --: 
Min | `r round(s_ShnabelRPP_varT[1], r.dec)` | `r round(s_ShnabelRPP_varE[1], r.dec)`
Q1  | `r round(s_ShnabelRPP_varT[2], r.dec)` | `r round(s_ShnabelRPP_varE[2], r.dec)`
Median| `r round(s_ShnabelRPP_varT[3], r.dec)` | `r round(s_ShnabelRPP_varE[3], r.dec)`
Q3  | `r round(s_ShnabelRPP_varT[4], r.dec)` | `r round(s_ShnabelRPP_varE[4], r.dec)`
Max | `r round(s_ShnabelRPP_varT[5], r.dec)` | `r round(s_ShnabelRPP_varE[5], r.dec)`
Mean| `r round(s_ShnabelRPP_varT[6], r.dec)` | `r round(s_ShnabelRPP_varE[6], r.dec)`

Performing a random-effects meta-analysis on the components directly leads to:

{} | True Score Variance | Error Score Variance
-- | -- | --:
Meta-Analytic Mean Estimate | `r round(s_ShnabelRPP_varT_rma$b[1], r.dec)` | `r round(s_ShnabelRPP_varE_rma$b[1], r.dec)`
Confidence Interval | `r round(s_ShnabelRPP_varT_rma$ci.lb, r.dec)` : `r round(s_ShnabelRPP_varT_rma$ci.ub, r.dec)` | `r round(s_ShnabelRPP_varE_rma$ci.lb, r.dec)` : `r round(s_ShnabelRPP_varE_rma$ci.ub, r.dec)`
Heterogeneity tau | `r round(sqrt(s_ShnabelRPP_varT_rma$tau2), r.dec)` | `r round(sqrt(s_ShnabelRPP_varE_rma$tau2), r.dec)`
Heterogeneity I^2 | `r round(s_ShnabelRPP_varT_rma$I2, r.dec)` | `r round(s_ShnabelRPP_varE_rma$I2, r.dec)`
Heterogeneity H^2 | `r round(s_ShnabelRPP_varT_rma$H2, r.dec)` | `r round(s_ShnabelRPP_varE_rma$H2, r.dec)`
Q(`r s_ShnabelRPP_varT_rma$k - 1`) | `r round(s_ShnabelRPP_varT_rma$QE, r.dec)` | `r round(s_ShnabelRPP_varE_rma$QE, r.dec)`
p-value QE | `r ifelse(s_ShnabelRPP_varT_rma$QEp < .001, "<.001", round(s_ShnabelRPP_varT_rma$QEp, r.dec))` | `r ifelse(s_ShnabelRPP_varE_rma$QEp < .001, "<.001", round(s_ShnabelRPP_varE_rma$QEp, r.dec))`










### Shnabel Sense of Power (Rev)


Comparing those results to the labs employing the revised protocol, score reliability varied between `r round(s_ShnabelRev_Alpha[1], r.dec)` and `r round(s_ShnabelRev_Alpha[6], r.dec)`, with a mean value of `r round(s_ShnabelRev_Alpha[4], r.dec)` and median value `r round(s_ShnabelRev_Alpha[3], r.dec)`. Performing a random-effects meta-analysis on the untransformed Cronbach’s Alpha estimates, we find a meta-analytic mean estimate of `r round(s_ShnabelRev_Alpha_rma$b[1], r.dec)` (`r round(s_ShnabelRev_Alpha_rma$ci.lb, r.dec)` : `r round(s_ShnabelRev_Alpha_rma$ci.ub, r.dec)`). Additionally, we find no significant degree of heterogeneity in score reliability, at Q(`r s_ShnabelRev_Alpha_rma$k - 1`) = `r round(s_ShnabelRev_Alpha_rma$QE, r.dec)`, p `r ifelse(s_ShnabelRev_Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_ShnabelRev_Alpha_rma$QEp, r.dec)))`. In terms of I^2, heterogeneity is `r round(s_ShnabelRev_Alpha_rma$I2, r.dec)`%, which, according to XXX constitutes a low to medium level of heterogeneity. In terms of tau, we find a standard deviation of `r round(sqrt(s_ShnabelRev_Alpha_rma$tau2), r.dec)` in true values of Cronbach’s Alpha. Similarly, when assessing Bonett-transformed Cronbach’s Alpha estimates, we find a meta-analytic mean of `r round(s_ShnabelRev_B.Alpha_rma$b[1], r.dec)`. Back-transformed this constitutes a Cronbach’s Alpha of `r round(1-exp(s_ShnabelRev_B.Alpha_rma$b[1]), r.dec)` (CI: `r round(1-exp(s_ShnabelRev_B.Alpha_rma$ci.ub), r.dec)` : `r round(1-exp(s_ShnabelRev_B.Alpha_rma$ci.lb), r.dec)`) (difference in MA-est. emerges at the 3rd decimal). Heterogeneity in Bonett-transformed estimates of Cronbach’s Alpha is of statistically significant degree: Q(`r s_ShnabelRev_Alpha_rma$k - 1`) = `r round(s_ShnabelRev_B.Alpha_rma$QE, r.dec)`, p `r ifelse(s_ShnabelRev_B.Alpha_rma$QEp < .001, "<.001", paste0("= ", round(s_ShnabelRev_B.Alpha_rma$QEp, r.dec)))`. Standardized heterogeneity estimates of I^2 = `r round(s_ShnabelRev_B.Alpha_rma$I2, r.dec)`% and H^2 = `r round(s_ShnabelRev_B.Alpha_rma$H2, r.dec)` display highly similar amounts of heterogeneity. 


Also, we use Cronbach's Alpha to decompose the observed variance into its true and error score variance components:

{}  | True Score Variance | Error Score Variance
-- | -- | --: 
Min | `r round(s_ShnabelRev_varT[1], r.dec)` | `r round(s_ShnabelRev_varE[1], r.dec)`
Q1  | `r round(s_ShnabelRev_varT[2], r.dec)` | `r round(s_ShnabelRev_varE[2], r.dec)`
Median| `r round(s_ShnabelRev_varT[3], r.dec)` | `r round(s_ShnabelRev_varE[3], r.dec)`
Q3  | `r round(s_ShnabelRev_varT[4], r.dec)` | `r round(s_ShnabelRev_varE[4], r.dec)`
Max | `r round(s_ShnabelRev_varT[5], r.dec)` | `r round(s_ShnabelRev_varE[5], r.dec)`
Mean| `r round(s_ShnabelRev_varT[6], r.dec)` | `r round(s_ShnabelRev_varE[6], r.dec)`

Performing a random-effects meta-analysis on the components directly leads to:

{} | True Score Variance | Error Score Variance
-- | -- | --:
Meta-Analytic Mean Estimate | `r round(s_ShnabelRev_varT_rma$b[1], r.dec)` | `r round(s_ShnabelRev_varE_rma$b[1], r.dec)`
Confidence Interval | `r round(s_ShnabelRev_varT_rma$ci.lb, r.dec)` : `r round(s_ShnabelRev_varT_rma$ci.ub, r.dec)` | `r round(s_ShnabelRev_varE_rma$ci.lb, r.dec)` : `r round(s_ShnabelRev_varE_rma$ci.ub, r.dec)`
Heterogeneity tau | `r round(sqrt(s_ShnabelRev_varT_rma$tau2), r.dec)` | `r round(sqrt(s_ShnabelRev_varE_rma$tau2), r.dec)`
Heterogeneity I^2 | `r round(s_ShnabelRev_varT_rma$I2, r.dec)` | `r round(s_ShnabelRev_varE_rma$I2, r.dec)`
Heterogeneity H^2 | `r round(s_ShnabelRev_varT_rma$H2, r.dec)` | `r round(s_ShnabelRev_varE_rma$H2, r.dec)`
Q(`r s_ShnabelRev_varT_rma$k - 1`) | `r round(s_ShnabelRev_varT_rma$QE, r.dec)` | `r round(s_ShnabelRev_varE_rma$QE, r.dec)`
p-value QE | `r ifelse(s_ShnabelRev_varT_rma$QEp < .001, "<.001", round(s_ShnabelRev_varT_rma$QEp, r.dec))` | `r ifelse(s_ShnabelRev_varE_rma$QEp < .001, "<.001", round(s_ShnabelRev_varE_rma$QEp, r.dec))`




